\mireval{}

### 2014-05-08 paper/paper.tex
Removing source separation and updating table

\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, onset detection, and source separation.
Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.

@@

\subsection{Source Separation}

@@

% Beat: Compared against MIREX 2013
% Chord: Compared against ??
% Segmentation: Compared against ??
% Melody: Compared against MIREX 2011, SG2 only
% Pattern: Compared against development set, MATLAB code
% Source Separation: Compared against SiSEC dev sets
% Onset: Compared against MIREX 2013

% Beat - 9 metrics
% Chord - 5 metrics
% Segmentation - 14 metrics
% Melody - 5 metrics
% Pattern - 21 metrics
% Onset - 3 metrics
% Source Separation - 3 metrics

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c c}
\toprule
 \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){5-10}
 Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
 ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \midrule
 \multicolumn{10}{ c }{Segmentation} \\
  \cmidrule(lr){1-10}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
  \midrule
 \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-10}
  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
  \midrule
 \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-10}
  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{10}{ c }{Pattern}\\
  \cmidrule(lr){1-10}
  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-7}
  \cmidrule(lr){8-10}
 Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
 ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
  \bottomrule

\end{tabular}
\end{table*}

>>>>

\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord recognition, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.

@@

@@

% Beat: Compared against MIREX 2013
% Chord: Compared against ??
% Segmentation: Compared against ??
% Melody: Compared against MIREX 2011, SG2 only
% Pattern: Compared against development set, MATLAB code
% Onset: Compared against MIREX 2013

% Beat - 9 metrics
% Chord - 5 metrics
% Segmentation - 14 metrics
% Melody - 5 metrics
% Onset - 3 metrics

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabular}
\begin{tabular}{c c c c c c c c c}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabular}
\begin{tabular}{c c c c c c c c}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabular}
\begin{tabular}{c c c c c c c c c c}
 \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
  ??? & ??? & ??? & ??? & ??? & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabular}
\end{table*}
